Abstract

### 2025-10-24 output/Main_text.Rmd
Correct use of "item" subindex explaining Figure 1
The {MDISC}_R references are to certain items' values, so the "item" subindex should not be used.

A comparison of panels (a) and (c) allows understanding the effect of
a positive correlation on the $`r MDISC_CORR_PARAM`$
(and consequently the $`r MIL_CORR_PARAM`$) value:
The components of the discrimination parameters tend to
*sum up* in the same direction as they get *more aligned*.
Thus, if the discrimination parameters have the same sign, as in items 1 and 5,
the $`r MDISC_CORR_PARAM_ITEM`$ value tends to increase;
on the contrary, when the discrimination parameters have opposite signs,
they tend to cancel each other out, and $`r MDISC_CORR_PARAM_ITEM`$ decreases,
as happens with items 2 and 3.
This effect can be especially noticed by comparing
the $`r MDISC_CORR_PARAM_ITEM`$ values of items 3 and 5:
Their discrimination parameters are equal in absolute value,
so their $`r MDISC_CORR_PARAM_ITEM`$ values are equal in the orthogonal space;
however, the effect of the correlation shrinks the former and
stretches the latter.
Finally, note that item 4 has one discrimination parameter equal to 0,
so its $`r MDISC_CORR_PARAM_ITEM`$ is unaffected by the correlation.

>>>>

A comparison of panels (a) and (c) allows understanding the effect of
a positive correlation on the $`r MDISC_CORR_PARAM`$
(and consequently the $`r MIL_CORR_PARAM`$) value of an item:
The components of the discrimination parameters tend to
*sum up* in the same direction as they get *more aligned*.
Thus, if the discrimination parameters have the same sign, as in items 1 and 5,
the $`r MDISC_CORR_PARAM`$ value tends to increase;
on the contrary, when the discrimination parameters have opposite signs,
they tend to cancel each other out, and $`r MDISC_CORR_PARAM`$ decreases,
as happens with items 2 and 3.
This effect can be especially noticed by comparing
the $`r MDISC_CORR_PARAM`$ values of items 3 and 5:
Their discrimination parameters are equal in absolute value,
so their $`r MDISC_CORR_PARAM`$ values are equal in the orthogonal space;
however, the effect of the correlation shrinks the former and
stretches the latter.
Finally, note that item 4 has one discrimination parameter equal to 0,
so its $`r MDISC_CORR_PARAM`$ is unaffected by the correlation.
